%Copyright 2014 Jean-Philippe Eisenbarth
%This program is free software: you can 
%redistribute it and/or modify it under the terms of the GNU General Public 
%License as published by the Free Software Foundation, either version 3 of the 
%License, or (at your option) any later version.
%This program is distributed in the hope that it will be useful,but WITHOUT ANY 
%WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A 
%PARTICULAR PURPOSE. See the GNU General Public License for more details.
%You should have received a copy of the GNU General Public License along with 
%this program.  If not, see <http://www.gnu.org/licenses/>.

%Based on the code of Yiannis Lazarides
%http://tex.stackexchange.com/questions/42602/software-requirements-specification-with-latex
%http://tex.stackexchange.com/users/963/yiannis-lazarides
%Also based on the template of Karl E. Wiegers
%http://www.se.rit.edu/~emad/teaching/slides/srs_template_sep14.pdf
%http://karlwiegers.com

%Modified for EECS 393 project in Spring 2017
%Dina Benayad-Cherif, Jason Dong, Mark Lalor, Yousef Mahmoud, Vimig Socrates
\documentclass{scrreprt}
\usepackage{listings}
\usepackage{underscore}
\usepackage{xcolor}
\usepackage[bookmarks=true]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\hypersetup{
    bookmarks=false,
    pdftitle={Software Design Document},
    pdfauthor={Dina Benayad-Cherif, Jason Dong, Mark Lalor, Yousef Mahmoud, Vimig Socrates},
    pdfsubject={EECS 393 Software Design Document},
    pdfkeywords={SRS, Software, Design},
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=blue,         % color of internal links
    citecolor=black,        % color of links to bibliography
    filecolor=black,        % color of file links
    urlcolor=purple,        % color of external links
    linktoc=page            % only page is linked
}

\addto\captionsenglish{\renewcommand{\contentsname}{Table Of Contents}}
\def\myversion{1.0}
\date{}

\usepackage{hyperref}
\begin{document}

% Title Page
\begin{flushright}
	\rule{16cm}{5pt}\vskip1cm
	\Huge{SOFTWARE DESIGN\\ DOCUMENT}\\
	\vspace{2cm}
	for\\
	\vspace{2cm}
	Class Collaboration Application (CCA)\\
	\vspace{2cm}
	\LARGE{Release \myversion \\}
	\vspace{2cm}
	Prepared by Dina Benayad-Cherif, Jason Dong, Mark Lalor, Yousef Mahmoud, Vimig Socrates\\
	\vfill
	\rule{16cm}{5pt}
\end{flushright}

\tableofcontents

%%%%%%%%%%%%%%%%
% INTRODUCTION %
%%%%%%%%%%%%%%%%

\chapter{Introduction}

\section{Purpose}

\section{Scope}

\section{Overview}

\section{Reference Material}

\begin{itemize}
	\item Book Inventory System System Design Document
	\item ZZZ Software Architecture
\end{itemize}

%%%%%%%%%%%%%%%%%%%
% SYSTEM OVERVIEW %
%%%%%%%%%%%%%%%%%%%

\chapter{System Overview}

%%%%%%%%%%%%%%%%%%%%%
% PRINCIPAL CLASSES %
%%%%%%%%%%%%%%%%%%%%%

\chapter{Principal Classes}
	
\section{}

\section{}

\section{}

%%%%%%%%%%%%%%%%%%%%%%%
% SYSTEM ARCHITECTURE %
%%%%%%%%%%%%%%%%%%%%%%%

\chapter{System Architecture}

\section{Architectural Design}

\section{Decomposition Description}

\section{Design Rationale}

%%%%%%%%%%%%%%%%%%%%
% CLASS INTERFACES %
%%%%%%%%%%%%%%%%%%%%

\chapter{Class Interfaces}

\section{Class Student}
An instance of Student represents a user who can create CourseItems and 		Courses. A student is also able to upload Documents attached to a CourseItem.
\subsection{Public Constructor Student}
\textit{Student(String name, String id, Time lastLogin)} \\
Creates a student object containing the name and Case ID.

\subsection{Public Method GetStudentID}
\textit{String GetStudentID()} \\
Returns the Case ID of the user.

\subsection{Public Method GetDurationOfSession}
\textit{Time GetDurationOfSession()} \\
Returns the length of the current login session of the user.

\subsection{Public Method IsSessionExpired}
\textit{Boolean IsSessionExpired()} \\
Returns whether the the current login session is expired.

\subsection{Public Method CreateCourseItem}
\textit{Boolean CreateCourseItem(dict options, Course course)} \\
Creates an instance of a CourseItem and returns whether it was 		successfully made.

\subsection{Public Static Method CreateCourse}
\textit{Boolean CreateCourse(String courseID, String CourseName)} \\
Creates an instance of a Course and returns whether it was			 successfully made.

\subsection{Public Method GetEnrolledCourses}
\textit{List<Course> GetEnrolledCourses()} \\
Returns the list of courses a student is currently enrolled in on the application.

\subsection{Public Method JoinCourse}
\textit{Boolean JoinCourse(Course course)} \\
Returns whether a student successfully joined to a preexisting course.

\section{Class Course}

\subsection{Public Method GetStudents}
\textit{List<Student> GetStudents()} \\
Queries the students table of the database to see which students 		have added this course to their list of courses.

\subsection{Public Method GetCourseItems()}
\textit{List<CourseItem> GetCourseItems()} \\
Queries the database to return a list of all CourseItems associated with the course.

\subsection{Public Method GetChat}
\textit{Chat GetChat()} \\
Returns the instance of the Chat class associated with the Course.

\section{Class CourseItem}
An object created by a student that can contain a document relevant to the course. This object is associated with a Course object.

\subsection{Public Method RemoveCourseItem}
\textit{Boolean RemoveCourseItem()} \\
Removes the CourseItem from the database, so that it is no longer available to Students.

\subsection{Public Method ModifyCourseItem}
\textit{Boolean ModifyCourseItem(Document document)} \\
Adds the document to the already existing CourseItem.

\section{Class Document}

\subsection{Public Method Download}
\textit{Void Download()} \\
Returns whether document was successfully downloaded to the user's machine.

\subsection{Public Method GetCourseItemID}
\textit{String GetCourseItemID()} \\
Returns the unique id associated with the course item.

\section{Class Chat}
Represents the chat for a course. The Chat object will hold all ChatMessage objects for a course.

\subsection{Public Method GetChatVersion}
\textit{Integer GetChatVersion()} \\
Returns what number message the chat has currently advanced to. This is cached whenever possible and queried often by the user to know when to request updates.

\subsection{Public Method GetChatMessages}
\textit{List<ChatMessage> GetChatMessages(Integer number = 50)} \\
Returns that last \textit{number} chat messages associated with this chat (default 50).

\subsection{Public Method SendMessage}
\textit{Void SendMessage(String content, Student author)} \\
Creates a ChatMessage object with a string content and sends it to the chat.

\subsection{Public Method SendDocument}
\textit{Void SendDocument(Document doc, Student author)} \\
Creates a ChatMessage object with a document attached and sends it to the chat.

\section{Class ChatMessage}
Represents a single message sent in a Chat. This message can be text or a document.

\subsection{Public Enum MessageType}
\textit{} \\
Indicates the chat message type. Currently can be:
\begin{itemize}
	\item Text
	\item Document
	\item Image
\end{itemize}

\subsection{Public Method GetType}
\textit{MessageType GetType()} \\
Returns the type of the message.

\subsection{Public Method GetContent}
\textit{Void GetContent()} \\
Returns the content associated with the ChatMessage.

\subsection{Private Method GetText()}
\textit{String GetText()} \\
Returns the text associated with this ChatMessage

\subsection{Private Method GetURL()}
\textit{String GetURL()} \\
Returns the URL associated with this ChatMessage.

\subsection{Public Method GetStudent}
\textit{Student GetStudent()} \\
Returns the Student who created the ChatMessage object.

\subsection{Public Method GetTime}
\textit{Time GetTime()} \\
Returns the time the ChatMessage object was sent.

\subsection{Public Method Delete()}
\textit{Void Delete()} \\
Removes the ChatMessage object from the database. This object will no longer be shown in the Chat object class.

%%%%%%%%%%%%%%%%%%%%%%%%%%
% HUMAN INTERFACE DESIGN %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Human Interface Design}

\section{Overview of User Interface}

\section{Screen Images}

\section{Screen Objects and Actions}


\end{document}
